---
title: "Wk5R_QZ"
author: "Riguel"
date: "07/02/2014"
output: html_document
---

**Indempotant Matrix** is when a matrix can be multiplied by itself and yields the same matrix.      



**Orthogonal** is when the transpose of the matrix is equals to its inverse.


###MatrixA

```{r Matrix A, fig.height=4, fig.width=4}
A <- matrix(c(1,-1,-1,-1),2)
A

#Indempotency of A
Aimp = A*A
Aimp

# inverse of A
Ai = solve(A)
Ai

# transpose of A
At = t(A)
At
```
**Matrix A is not Indempotent**


**Matrix A is not Orthogonal**


###Matrix B

```{r Matrix B, fig.height=4, fig.width=4}
B <- matrix(c(2,-1,3,-2),2)
B

#Indempotency of B
Bimp = B*B
Bimp

# inverse of B
Bi = solve(B)
Bi

# transpose of B
Bt = t(B)
Bt
```
**Matrix B is not Indempotent**

**Matrix B is not Orthogonal**

###Matrix C

```{r Matrix C, fig.height=4, fig.width=4}
C <- matrix(c(1,0,0,0),2)
C

#Indempotency of C
Cimp = C*C
Cimp

# inverse of C connot be done


# transpose of C
Ct = t(C)
Ct
```
**Matrix C is Indempotent**


**Matrix C is not Orthogonal**


###Matrix D

```{r Matrix D, fig.height=4, fig.width=4}
D <- matrix(c(0,1,0,1,0,0,0,0,1),3)
D

#Indempotency of D
Dimp = D*D
Dimp

# inverse of D
Di = solve(D)
Di

# transpose of D
Dt = t(D)
Dt
```

**Matrix D is Indempotent**


**Matrix D is Othogonal**


###Matrix E

```{r Matrix E, fig.height=4, fig.width=4}
E <- matrix(c(1,0,0,0,0,1,0,1,0),3)
E

#Indempotency of E
Eimp = E*E
Eimp

# inverse of E
Ei = solve(E)
Ei

# transpose of E
Et = t(E)
Et

```
**Matrix E is Indempotent**


**Matrix E is Othogonal**


##List with five different Structures

###Vector

```{r Vector, fig.height=4, fig.width=4}
Vect <-c(1:10)
Vect
```


###Matrix

```{r Matrix, fig.height=4, fig.width=4}
Mtrx <- matrix(c(1,0,0,0,0,1,0,1,0),3)
Mtrx
```

###Array

```{r Array, fig.height=4, fig.width=4}
Arr <- array(1:12, dim = c(2,3,4))
Arr
```

###Data Frame

```{r Data Frame, fig.height=4, fig.width=4}
x <- 1:10
y <- -4:5
z <- -1:-10
DF <- data.frame(x,y,z)
DF
```


###List 

```{r List, fig.height=4, fig.width=4}
lst <- list(1,2,3)
lst
```


###List with the five structures 

```{r List5, fig.height=4, fig.width=4}
list5 <- list(Vect,Mtrx,Arr,DF,lst)
list5
```